\myfont Implementation and evaluation of register allocation for translating LLVM-{}- to x86-64

### 2024-01-12 article.tex
Explain bug

as can be seen in Figure \ref{fig:intervals-ocaml}.

@@

>>>>

%as can be seen in Figure \ref{fig:intervals-ocaml}.

@@

One particularly nasty oversight that was discovered a couple of days prior to handin stems from phi movs overwriting each other.
Consider Figure \ref{fig:sqrt1.ll} where two phi instructions either move \texttt{\%6} to \texttt{label \%10} or \texttt{\%7} to \texttt{label \%5} depending on the condition. In some cases, even in greedy where each variable is assigned their own discrete register, their respective values are overwritten. This is due to \texttt{\%7} being moved to \texttt{\%6} prior to potentially branching back to \texttt{label \%5}. If phi moves are conducted unconditionally of branch condition \texttt{\%9}, the value of \texttt{\%6} prior to branching to \texttt{label \%10} is overwritten on the off-chance of returning to \texttt{label \%5}, causing the value assigned to \texttt{\%11} and returned on line 10 to always be equal to \texttt{\%7} instead of the intended \texttt{\%7} instead of the intended  \texttt{\%6}.

\begin{figure}[H]
   \begin{minipage}{0.58\textwidth}
     \centering
     \begin{minted}[linenos,bgcolor=LightGray]{llvm}
 ; ...
5:
 %6 = phi i32 [%7, %5], [1, %3]
 %7 = add i32 %6, 1
 %8 = mul i32 %7, %7
 %9 = icmp sgt i32 %8, %0
 br i1 %9, label %10, label %5
10:
 %11 = phi i32 [%0, %1], [0, %3], [%6, %5]
 ret i32 %11
}
     \end{minted}
     \caption{\texttt{dune exec build -{}- -t x86}}\label{fig:sqrt1.ll}
   \end{minipage}
   \begin{minipage}{0.40\textwidth}
     \centering
     \begin{minted}[linenos,bgcolor=LightGray]{gas}
# ...
# br i1 %9, label %10, label %5
movq	%r10, %rax
cmpq	$0, %rax
movq	%r8, %rax
movq	%rax, %rdi
je	_isqrt$5
movq	%rdi, %rax
movq	%rax, %r11
jmp	_isqrt$10
# ...
     \end{minted}
     \caption{TODO}\label{fig:sqrt1.s}
   \end{minipage}
\end{figure}
This was resolved by relying on conditional movs immediately prior to branching conditionally. Specifically, the \texttt{cmoveq} instruction was used, which only moves the value if the equals flag (i.e. \texttt{ZF}) is set.
